HPC--101\\Onboarding

### 2021-03-09 hpc_101/sections/01_intro.tex
update to slides to have a full version (online) and a presentation version.
Next steps are to make it simpler to generate both versions

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster - \textbf{\mana} (formerly~known~as~the~{\uhhpc}) is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased by faculty \& staff
    \end{itemize}
		\begin{block}{Mana Resource Summary}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home/Group Space}} & \thead{\textbf{Scratch Space}} & Storage for lease \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 298                    & 6,308                      & 50 TB                   &  64                   & 80 TB                             &  150 TB                        & 1 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

\subsection{Condo Program \& Leasing}
\begin{frame}
  \frametitle{What is the Condo Program \& leasing?}
	\begin{block}{Condo Program}\scriptsize
		\begin{itemize}
		\item The condo program allows faculty \& staff to purchase nodes and have them integrated with {\mana}
		\item Condo nodes can take advantage of networking and storage infrastructure that one may not typically have access to
		\item Condo nodes are managed and maintained by ITS staff
		\item No maintenance fee will be assessed until the node is off warranty (typically five years)
		\end{itemize}
	\end{block}
	\begin{block}{Leasing}\scriptsize
		\begin{itemize}
		\item Nodes leased from the community can have a contract period from one month, up to one year
		\item Node lessees are provided priority access to their leased hardware
		\item Leases are not considered an equipment purchase
		\end{itemize}
	\end{block}
\end{frame}

\subsection{Storage}
\begin{frame}
  \frametitle{Storage}
  {\mana} has two classes and three types of storage that users can potentially access.\\Each type of storage has their own attributes and restrictions
	\begin{columns}
		\begin{column}{0.46\textwidth}
		\begin{block}{Free Storage}
			\begin{enumerate}
			\item Permanent Storage
				\begin{itemize}
				\item Home Storage
				\item Group/Lab Storage
				\end{itemize}
			\item Scratch Storage
				\begin{itemize}
%				\item {\lustre}(TBD)
				\item Network File System (NFS)
				\end{itemize}
		\end{enumerate}
		\end{block}
		\end{column}
		\begin{column}{0.46\textwidth}
		\begin{block}{For Fee Storage}
			\begin{enumerate}
				\item Long Term Storage (LTS)
		\end{enumerate}
		\end{block}
		\end{column}
	\end{columns}      
\end{frame}

@@

\begin{frame}
  \frametitle{Scratch Storage}
  \begin{enumerate}
%    \item {\lustre (TBD)}
%      \begin{itemize}
%      \item High performance parallel file system 
%      \item 50 TB quota
%      \end{itemize}
    \item NFS
      \begin{itemize}
%      \item Not a parallel file system
      \item 5 TB quota
      \end{itemize}
  \end{enumerate}
~\\
  Scratch file systems on {\mana} have the following attributes:
  \begin{itemize}
  \item \textbf{Purge policy} -- 10 days based on file modify time
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

\subsection{Networking}
\begin{frame}
  \frametitle{Networking}
	\begin{columns}
	\begin{column}{0.46\textwidth}
		\begin{block}{Internal Networks}
		\begin{itemize}
			\item Quad Data Rate (QDR)\\InfiniBand{\regtrademark} (IB)   
				\begin{itemize}
					\item 40 Gbit
					\item Older compute nodes
					\item low latency ($\approx1.3\mu$s)
					\item non-blocking
				\end{itemize}
				~\\
			\item 25/100 Gbit Ethernet
				\begin{itemize}
					\item Newer compute nodes
					\item Nodes connected @ 25~Gbit
					\item non-blocking
				\end{itemize}
	        \end{itemize}
                \end{block}
	\end{column}
	\begin{column}{0.46\textwidth}
		\begin{block}{External Networks}
		\begin{itemize}
			\item 100 Gbit SciDMZ
				\begin{itemize}
					\item Login \& compute nodes\\connected via a firewall
					\item DTNs are directly connected
				\end{itemize}
		\end{itemize}
                \end{block}
	\end{column}
	\end{columns}
\end{frame}

@@

>>>>

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster - \textbf{\mana} is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased by faculty \& staff
    \end{itemize}
		\begin{block}{Mana Resource Summary}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home/Group Space}} & \thead{\textbf{Scratch Space}} & \thead{\textbf{Storage for lease}} \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 345                    & 8,452                      & 62.9 TB                   &  120                   & 80 TB                             &  211 TB                        & 1 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

\subsection{Storage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{frame}
  %\frametitle{Storage}
  %{\mana} has two classes and three types of storage that users can potentially access.\\Each type of storage has their own attributes and restrictions
	%\begin{columns}
		%\begin{column}{0.46\textwidth}
		%\begin{block}{Free Storage}
			%\begin{enumerate}
			%\item Permanent Storage
				%\begin{itemize}
				%\item Home Storage
				%\item Group/Lab Storage
				%\end{itemize}
			%\item Scratch Storage
				%\begin{itemize}
				%\item {\lustre}
				%\item Network File System (NFS)
				%\end{itemize}
		%\end{enumerate}
		%\end{block}
		%\end{column}
		%\begin{column}{0.46\textwidth}
		%\begin{block}{For Fee Storage}
			%\begin{enumerate}
				%\item Long Term Storage (LTS)
		%\end{enumerate}
		%\end{block}
		%\end{column}
	%\end{columns}      
%\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{frame}
  \frametitle{Scratch Storage}
  \begin{enumerate}
    \item {\lustre}
      \begin{itemize}
			\item A parallel distributed file system 
      \end{itemize}
    \item NFS
      \begin{itemize}
			\item A distributed file system 
      \end{itemize}
  \end{enumerate}
~\\
  Scratch file systems on {\mana} have the following attributes:
  \begin{itemize}
	\item 5 TB quota
  \item \textbf{Purge policy} -- 10 days based on file modify time
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\subsection{Networking}
%\begin{frame}
  %\frametitle{Networking}
	%\begin{columns}
	%\begin{column}{0.46\textwidth}
		%\begin{block}{Internal Networks}
		%\begin{itemize}
			%\item Quad Data Rate (QDR)\\InfiniBand{\regtrademark} (IB)   
				%\begin{itemize}
					%\item 40 Gbit
					%\item low latency ($\approx1.3\mu$s)
					%\item non-blocking
				%\end{itemize}
			%\item High Data Rate (HDR) IB   
				%\begin{itemize}
					%\item 100 Gbit
					%\item low latency ($\approx0.5\mu$s)
					%%\item non-blocking
				%\end{itemize}
			%\item 1/25/100 Gbit Ethernet
%
	        %\end{itemize}
                %\end{block}
	%\end{column}
	%\begin{column}{0.46\textwidth}
		%\begin{block}{External Networks}
		%\begin{itemize}
			%\item 100 Gbit SciDMZ
				%\begin{itemize}
					%\item Login \& compute nodes\\connected via a firewall
					%\item DTNs are directly connected
				%\end{itemize}
		%\end{itemize}
                %\end{block}
	%\end{column}
	%\end{columns}
%\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Condo Program \& Leasing}
\begin{frame}
  \frametitle{What is the Condo Program \& leasing?}
	\begin{block}{Condo Program}\scriptsize
		\begin{itemize}
		\item The condo program allows faculty \& staff to purchase nodes and have them integrated with {\mana}
		\item Condo nodes can take advantage of networking and storage infrastructure that one may not typically have access to
		\item Condo nodes are managed and maintained by ITS staff
		\item Nodes are purchased with a five year warranty
		\end{itemize}
	\end{block}
	\begin{block}{Leasing}\scriptsize
		\begin{itemize}
		\item Nodes leased from the community can have a contract period from one month, up to one year
		\item Node lessees are provided priority access to their leased hardware
		\item Leases are not considered an equipment purchase
		\end{itemize}
	\end{block}
\end{frame}
